Donor Responses to Civil Society Repression

### 2024-11-05 README.qmd
Add badges for HTML and PDF

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2F9gmhp-blue)](https://doi.org/10.31235/osf.io/9gmhp) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FR97Y3-blue)](https://doi.org/10.17605/OSF.IO/R97Y3) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![HTML preprint](https://img.shields.io/badge/HTML%20preprint-FF851B)](https://stats.andrewheiss.com/butterscotch-bat/manuscript.html) [![PDF preprint](https://img.shields.io/badge/PDF%20preprint-3D9970)](https://stats.andrewheiss.com/butterscotch-bat/manuscript.pdf) [![SocArXiv Preprint](https://img.shields.io/badge/SocArXiv%20preprint-10.31235%2Fosf.io%2F9gmhp-blue)](https://doi.org/10.31235/osf.io/9gmhp) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FR97Y3-blue)](https://doi.org/10.17605/OSF.IO/R97Y3) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14038467-blue)](https://doi.org/10.5281/zenodo.14038467)
<!-- badges: end -->
